A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-01 sections/Metatheory.tex
S4 develop, dev -> development, developers

% ---------------------------------------------
\subsection{Abella and Proof Statistics}
We have chosen the Abella (v2.0.7-dev
\footnote{A develop version is used because the dev just fixed a serious bug that
accepts a simple proof of false, which also affects the completeness of our proof.
The author compiled the scripts against commit 92829a of the GitHub repository of Abella.}
) proof assistant~\cite{AbellaDesc} to develop our formalization.
Abella is designed to help with such formalizations of programming languages,
due to its built-in support for variable binding and
the $\lambda$-tree syntax~\cite{miller2000abstract}, i.e. a form of HOAS.
Nominal variables, or $\nabla$-quantified variables, are used as an unlimited name supply,
which supports explicit freshness control and substitutions.
Although Abella lacks packages, tactics and support on modules,
its higher-order unification and the ease of formalizing substitution-intensive relations
are very helpful for our formalization.

>>>>

% ---------------------------------------------
\subsection{Abella and Proof Statistics}
We have chosen the Abella (v2.0.7-dev
\footnote{A development version is used because the developers
just fixed a serious bug that accepts a simple proof of false,
which also affects the completeness of our proof.
The author compiled the scripts against commit 92829a of the GitHub repository of Abella.}
) proof assistant~\cite{AbellaDesc} to develop our formalization.
Abella is designed to help with such formalizations of programming languages,
due to its built-in support for variable binding and
the $\lambda$-tree syntax~\cite{miller2000abstract}, i.e. a form of HOAS.
Nominal variables, or $\nabla$-quantified variables, are used as an unlimited name supply,
which supports explicit freshness control and substitutions.
Although Abella lacks packages, tactics and support on modules,
its higher-order unification and the ease of formalizing substitution-intensive relations
are very helpful for our formalization.
